---
# title: "Single Promotion"
# author: "Toxic Bears"
# date: "12/08/2020"
output: html_document
params:
  song: "Misspent Youth"
  station_name: "2xx"
---


```{r setup, include=FALSE}
# This code block loads in the data sets and subsets the data using the parameters in the header above
library(dplyr)
knitr::opts_chunk$set(echo = TRUE)
song <- read.csv(file = "C:/Users/Prime/Desktop/R Projects/radio_mailer/data/Song_info.csv")
stations <- read.csv(file = "C:/Users/Prime/Desktop/R Projects/radio_mailer/data/Station_info.csv")
song_subset <- song %>% 
  filter(Track == params$song)
station_subset <- stations %>% 
  filter(Station == params$station_name)
```

```{r variable_define, include=FALSE }
md_name <- as.vector(station_subset[1], mode = "character")
track_name <- as.vector(song_subset[1], mode = "character")
radio_station <- as.vector(station_subset[3], mode = "character")
track_type <- as.vector(song_subset[2], mode = "character")
track_desc <- as.vector(song_subset[4], mode = "character")
program_type <- as.vector(song_subset[3], mode = "character")
location <- as.vector(station_subset[4], mode = "character")
download <- as.vector(song_subset[5], mode = "character")
YT_stream <- as.vector(song_subset[6], mode = "character")
smarturl <- as.vector(song_subset[7], mode = "character")
engineer <- as.vector(song_subset[8], mode = "character")
studio <- as.vector(song_subset[9], mode = "character")
email <- as.vector(station_subset[6], mode = "character")
```

### Email: 
`r email`
<br>
<br>

### Subject: 
New single released by Toxic Bears - `r track_name`
<br>
<br>

### Body:

Hi `r md_name`,

I'm from the Brisbane based avant-garage experimental rock band, Toxic Bears. 
On 23 December we will release a new single called `r track_name`, and would love to have it heard on `r radio_station`!   `r track_name` is an `r track_type` track about `r track_desc`. 
<br>
<br>

#### About the track

This track would suit programming that focuses on `r program_type`, as well as those that feature new and/or `r location` music. `r track_name` was mixed and mastered by `r engineer` from `r studio`.

You can download the track here:

`r download`
<br>
<br>

Alternatively, you can stream via Bandcamp here:

`r smarturl`
<br>
<br>

#### About the band

Toxic Bears are an experimental rock band based in Brisbane, Australia. Our music ranges from melodic hardcore to funk, jazz and Latin-infused garage rock. We’ve recorded three albums, an EP, and recently released three singles. We record all instrumentation live in a single take and only overdub vocals and other embellishments.   For more information, please visit  https://toxicbears.com/ 

It would be much appreciated if you could forward this track to the relevant producer/DJs at your radio station for their consideration and inclusion in their programming.

Thank you for your consideration and please don't hesitate to contact me if you have any further questions about the track or our band.

Best regards,

Mark

